---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# datasets

<!-- badges: start -->
<!-- badges: end -->

The goal of datasets is to provide a home for data sets for my courses, from various textbooks. I favour text files, but I grab what I can.

## example

Load Tidyverse first:

```{r}
library(tidyverse)
```


The data set `deprived` from Utts and Heckard is from a survey of students from a statistics class. Each student was asked whether they generally felt sleep-deprived or not, and also how many hours they usually slept per night:

```{r}
load("utts-heckard/deprived.rdata")
deprived
```

One would imagine that sleep-deprived people got less sleep:

```{r}
ggplot(deprived, aes(x=d, y=s)) + geom_boxplot()
```

There are outliers in both groups, but the answer appears to be yes. Is that significant?

```{r}
t.test(s~d, data=deprived, alternative="greater")
```

Yes, although it might be good to be concerned about the outliers.

